Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
Intro e Acknowledgements

@@

\begin{acknowledgments}
This work was supported by DOE contract No. DE-AC05-06OR23177,
under which Jefferson Science Associates, LLC operates Jefferson Lab, by the DOE contract DE-SC008791 and 
by the Joint Research Activity ``Study of Strongly
Interacting Matter'' (acronym HadronPhysics3, Grant Agreement No. 283286) under
the 7th Framework Programme of the European Community.
\end{acknowledgments}

>>>>

The nucleon tensor charge is a fundamental property of the nucleon that is at
the moment poorly constrained. There are several estimates based on lattice
QCD, but only a few estimates based on extractions from data. The main problem

@@

\begin{acknowledgments}
This work was supported by DOE contract No. DE-AC05-06OR23177,
under which Jefferson Science Associates, LLC operates Jefferson Lab, by the DOE contract DE-SC008791 and 
by the European Research Council (ERC) under the European Union's 
Horizon 2020 research and innovation programme (grant agreement No. 647981,
3DSPIN)
\end{acknowledgments}
